Postdoctoral Researcher

### 2016-09-13 NPCProposal2016/CV_Shih-Kai_Lin.tex
CV finished with 2-page restriction

\name{Shih-Kai}{Lin}
\title{Research Assistant}
\address{2121 El Paseo St Apt 1307}{Houston, TX, 77054}
\phone[mobile]{+1~(832)~907~9035}
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{shihkailin78@gmail.com}
%\homepage{www.johndoe.com}
\social[linkedin]{shihkailin}
%\social[twitter]{jdoe}
%\social[github]{jdoe}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}
\quote{}

@@

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{Sept. 2014}{Doctor of Philosophy in Physics}{University of Houston}{Houston, TX}{\textit{GPA: 3.867/4.0}}{}
\cventry{2003--2005}{Master of Science in Physics}{National Taiwan University}{Taipei, Taiwan}{}{}
\cventry{1996--2001}{Bachelor of Science in Computer Science}{National Taiwan University}{Taipei, Taiwan}{}{}

@@

\section{Experience}
\subsection{Vocational}
\cventry{2009--present}{Research Assistant}{University of Houston}{Houston, TX}{}{Member of particle physics group and Daya Bay Reactor Neutrino Experiment. Actively participated in the muon detector system QC/QA, installation, commissioning, operation and data analysis.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
	\item	Analyze data for neutron production by cosmic ray muons.
  \item Developed a reconstruction algorithm to reconstruct the incident position and the track of cosmic ray muons.
	\item Designed and built a small resistive plate chamber for monitoring the gas composition.
  \item Experience in operating radioactive sources such as $^{137}$Cs, $^{90}$Sr and $^{60}$Co for resistive plate chamber response study.
  \item Designed and built a collimator for shielding and collimating $^{60}$Co.
  \item Monte Carlo simulation on photoelectron production by photons and electron transport in Bakelite.
  \item Developed a web based 3D muon event display with WebGL and MySQL technology.
  \item During hardware installation, led a team of technicians to route 400 electronic cables from a 10m deep pool to the electronics control room in a week.
\end{itemize}}
\cventry{2005--2008}{Research Assistant}{Academia Sinica}{Taipei, Taiwan}{}{Joined Taiwan Experiment on Neutrino(TEXONO) group and worked on high purity Germanium detector response to different particles, energy calibration and data analysis.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
	\item Analyzed data used for dark matter exclusion plots.
	\item Calibrated the Ge detector with $^{137}$Cs, $^{60}$Co, $^{55}$Fe, $^{32}$P, etc.
	\item Maintained the Ge detector located 28m away from the core of No.1 reactor of Kuo-Sheng Nuclear Power Station.
  \item Utilizing pulse shape discrimination(PSD) technique to lower detector threshold.
  \item Developed an algorithm utilizing Fast Fourier Transform spectra to reject near-threshold detector noise.
\end{itemize}}
\cventry{2003--2005}{Research Assistant}{National Taiwan University}{Taipei, Taiwan}{}{Joined semiconductor group and worked on electron transport properties of Indium Gallium Nitride.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
  \item Measured and published a paper on the transport properties of Indium Gallium Nitride.
  \item Extensive experience in high vacuum and low temperature experiments.
\end{itemize}}
\cventry{2001--2003}{Lieutenant}{Mandatory Military Service}{}{}{Maintained and developed a windows application for database management of parts of radio equipment with Borland Delphi.\newline{}%
}
\subsection{Teaching}
\cventry{2004}{Teaching Assistant}{National Taiwan University}{Taipei, Taiwan}{}{Responsible for grading, solving and answering questions about University Physics homework problems for about 50 students.}

\section{Honors and Professional Memberships}
\cvitem{Mar 2013}{American Physical Society}
\cvitem{Nov 2009}{Golden Key International Honour Society}
\cvitem{2005}{Government Fellowship for Studying Abroad from Ministry of Education, Taiwan}

\section{Conference Talks}
\cvitem{Apr 2013}{Shih-Kai Lin, ``A Geometric Method for Measuring Muon Induced Neutrons at Daya Bay", APS April Meeting 2013}

\section{Languages}
\cvitem{Chinese}{Native}
\cvitem{English}{Fluent}

\section{Computer Skills}

\cvitem{Language}{\textsc{C/C++}, \textsc{MS Visual C++ 4.0}, \textsc{Borland Delphi}, \textsc{HTML}, \textsc{Python}, \textsc{Bash}, SQL, \textsc{JavaScript}, PHP, AJAX, \LaTeX}

\cvitem{Software}{\textsc{MySQL}, \textsc{SQLite}, \textsc{phpMyAdmin}, \textsc{Apache}, \textsc{Squid}, \textsc{Origin}, MATLAB}
\cvitem{System}{\textsc{Windows}, \textsc{Linux} (both \textsc{Debian} and \textsc{Red Hat} based)}

\section{Publications}
\cvitem{2013}{Z. Ning, Q.M. Zhang, J.L. Xu, L. Lebanowski, J.W. Zhang, C.G. Yang, M. He, J. Zhao, J.H. Zou, V. P{\v e}{\v c}, \underline{\textbf{\emph{Sh.-K. Lin}}}, M.Y. Guan, H.F. Hao, L. Zheng, X.L. Ji, F. Li, K. Lau and V. Vorobel, ``Calibration algorithms of RPC detectors at Daya Bay Neutrino Experiment", \textit{JINST} 8 (2013) T03007}

@@

\cvitem{2011}{Liehua Ma, Logan Lebanowski, Jin Chen, Mengyun Guan, Robert Hackenburg, Kwong
Lau, \underline{\textbf{\emph{Shih-Kai Lin}}}, Changguo Lu, Kirk McDonald, Cullen Newsom, Zhe Ning, Viktor Pec,
Sen Qian, Vit Vorobel, Yifang Wang, Jilei Xu, Changgen Yang, Jiawen Zhang, Qingmin
Zhang, “The mass production and quality control of RPCs for the Daya Bay experiment”,
\textit{Nuclear Instruments and Methods in Physics Research A} 659 (2011) 154–160}

\cvitem{2010}{M. Deniz, S.T. Lin, V. Singh, J. Li, H.T. Wong, S. Bilmis, C.Y. Chang, H.M. Chang, W.C. Chang, C.P. Chen, M.H. Chou, K.J. Dong, J.M. Fang, C.H. Hu, G.C. Jon, W.S. Kuo, W.P. Lai, F.S. Lee, S.C. Lee, H.B. Li, H.Y. Liao, C.W. Lin, F.K. Lin, \underline{\textbf{\emph{S.K. Lin}}}, Y. Liu, J.F. Qiu, M. Serin, H.Y. Sheng, L. Singh, R.F. Su, W.S. Tong, J.J. Wang, P.L. Wang, S.C. Wu, S.W. Yang, C.X. Yu, Q. Yue, M. Zeyrek, D.X. Zhao, Z.Y. Zhou, Y.F. Zhu, and B.A. Zhuang, ``Measurement of $\bar{\nu}_e$-elelctron cross section with a CsI(Tl) scintillating crystal array at the Kuo-Sheng nuclear power reactor", \textit{Phys. Rev. D} 81, 072001 (2010)}

\cvitem{2009}{S.T. Lin, H.B. Li, X. Li, \underline{\textbf{\emph{S.K. Lin}}}, H.T. Wong, M. Deniz, B.B. Fang, D. He, J. Li, C.W. Lin, F.K.
Lin, V. Singh, X.C. Ruan, J.J. Wang, Y.R. Wang, S.C. Wu, Q. Yue, and Z.Y. Zhou, “New limits
on spin-independent and spin-dependent couplings of low-mass WIMP dark matter with
a germanium detector at a threshold of 220 eV”, \textit{Phys. Rev. D} 79:061101, 2009}

\cvitem{2008}{H Y Liao, H M Chang, M H Chou, M Deniz, H X Huang, F S Lee, H B Li, J Li, C W Lin, F K Lin, \underline{\textbf{\emph{S K Lin}}}, S T Lin, V Singh, H T Wong and S C Wu, ``Production and decay of the $^{73}$Ge*(1/2$^-$) metastable state in a low-background germanium detector", \textit{J. Phys. G: Nucl. Part. Phys.} 35 (2008) 077001}

\cvitem{2007}{H. T. Wong, H. B. Li, S. T. Lin, F. S. Lee, V. Singh, S. C. Wu, C.Y. Chang, H. M. Chang, C. P.
Chen, M. H. Chou, M. Deniz, J. M. Fang, C. H. Hu, H. X. Huang, G. C. Jon, W. S. Kuo, W. P.
Lai, S. C. Lee, J. Li, H.Y. Liao, F. K. Lin, \underline{\textbf{\emph{S. K. Lin}}}, J. Q. Lu, H.Y. Sheng, R. F. Su, W. S. Tong, B.
Xin, T. R. Yeh, Q. Yue, Z.Y. Zhou, and B. A. Zhuang, “Search of Neutrino Magnetic
Moments with a High-Purity Germanium Detector at the Kuo-Sheng Nuclear Power
Station”, \textit{Phys. Rev. D} 75:012001, 2007}
\cvitem{2005}{\underline{\textbf{\emph{Shih-Kai Lin}}}, Kun-Ta Wu, Chao-Ping Huang, C.-T. Liang, Y. H. Chang, Y. F. Chen, P. H.
Chang, N.C. Chen, H. C. Peng, C. F. Shih, K. S. Liu and T. Y. Lin, ``Electron Transport in In-rich In$_x$Ga$_{1-x}$N films", \textit{Journal of Applied Physics} 97, 046101 (2005)}

>>>>

\name{Shih-Kai}{Lin}
\title{Postdoctoral Researcher}
\address{1700 W Plum St Apt 53E}{Fort Collins, CO, 80521}
\phone[mobile]{+1~(832)~907~9035}
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{Shihkai.Lin@colostate.edu}
%\homepage{www.johndoe.com}
\social[linkedin]{shihkailin}
%\social[twitter]{jdoe}
%\social[github]{jdoe}
%\extrainfo{additional information}
%\photo[64pt][0.4pt]{picture}
\quote{}

@@

\section{Education}
%\cventry{year--year}{Degree}{Institution}{City}{\textit{Grade}}{Description}
\cventry{Sept. 2014}{Doctor of Philosophy in Physics}{University of Houston}{Houston, TX}{}{}%{\textit{GPA: 3.867/4.0}}{}
\cventry{2003--2005}{Master of Science in Physics}{National Taiwan University}{Taipei, Taiwan}{}{}
\cventry{1996--2001}{Bachelor of Science in Computer Science}{National Taiwan University}{Taipei, Taiwan}{}{}

@@

\section{Experience}
%\subsection{Vocational}
\cventry{2014--present}{Postdoctoral Researcher}{Colorado State University}{Fort Collins, CO}{}{Member of the NOvA and the 35-ton prototype collaboration at FNAL.
\begin{itemize}
  \item Measuring $\bar{\nu}_\mu$ charged-current inclusive cross section with the NOvA near detector.
  \item Developed the control application for the LBNE calibration module for photon detector, which was used in 35-ton prototype's data taking.
  \item Photon detector R\&D and performance study.
\end{itemize}}
\cventry{2009--2014}{Research Assistant}{University of Houston}{Houston, TX}{}{Member of particle physics group and Daya Bay Reactor Neutrino Experiment. Actively participated in the muon detector system QC/QA, installation, commissioning, operation and data analysis.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
  \item	Analyzed data for neutron production by cosmic ray muons.
  \item Developed a reconstruction algorithm to reconstruct the incident position and the track of cosmic ray muons.
  \item Designed and built a small resistive plate chamber for monitoring the gas composition.
  \item Experience in operating radioactive sources such as $^{137}$Cs, $^{90}$Sr and $^{60}$Co for resistive plate chamber response study.
  \item Designed and built a collimator for shielding and collimating $^{60}$Co.
  \item Monte Carlo simulation on photoelectron production by photons and electron transport in Bakelite.
%  \item Developed a web based 3D muon event display with WebGL and MySQL technology.
%  \item During hardware installation, led a team of technicians to route 400 electronic cables from a 10m deep pool to the electronics control room in a week.
\end{itemize}}
\cventry{2005--2008}{Research Assistant}{Academia Sinica}{Taipei, Taiwan}{}{Joined Taiwan Experiment on Neutrino(TEXONO) group and worked on high purity Germanium detector response to different particles, energy calibration and data analysis.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
	\item Analyzed data used for dark matter exclusion plots.
	\item Calibrated the Ge detector with $^{137}$Cs, $^{60}$Co, $^{55}$Fe, $^{32}$P, etc.
	\item Maintained the Ge detector located 28m away from the core of No.1 reactor of Kuo-Sheng Nuclear Power Station.
  \item Utilizing pulse shape discrimination(PSD) technique to lower detector threshold.
  \item Developed an algorithm utilizing Fast Fourier Transform spectra to reject near-threshold detector noise.
\end{itemize}}
\cventry{2003--2005}{Research Assistant}{National Taiwan University}{Taipei, Taiwan}{}{Joined semiconductor group and worked on electron transport properties of Indium Gallium Nitride.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
  \item Measured and published a paper on the transport properties of Indium Gallium Nitride.
  \item Extensive experience in high vacuum and low temperature experiments.
\end{itemize}}
%\cventry{2001--2003}{Lieutenant}{Mandatory Military Service}{}{}{Maintained and developed a windows application for database management of parts of radio equipment with Borland Delphi.\newline{}%
%}
%\subsection{Teaching}
%\cventry{2004}{Teaching Assistant}{National Taiwan University}{Taipei, Taiwan}{}{Responsible for grading, solving and answering questions about University Physics homework problems for about 50 students.}

\section{Honors and Professional Memberships}
\cvitem{Nov 2015}{The 2016 Breakthrough Prize in Fundamental Physics}
\cvitem{Mar 2013}{American Physical Society}
\cvitem{Nov 2009}{Golden Key International Honour Society}
\cvitem{2005}{Government Fellowship for Studying Abroad from Ministry of Education, Taiwan}

%\section{Conference Talks}
%\cvitem{Apr 2013}{Shih-Kai Lin, ``A Geometric Method for Measuring Muon Induced Neutrons at Daya Bay", APS April Meeting 2013}

%\section{Languages}
%\cvitem{Chinese}{Native}
%\cvitem{English}{Fluent}

%\section{Computer Skills}
%
%\cvitem{Language}{\textsc{C/C++}, \textsc{MS Visual C++ 4.0}, \textsc{Borland Delphi}, \textsc{HTML}, \textsc{Python}, \textsc{Bash}, SQL, \textsc{JavaScript}, PHP, AJAX, \LaTeX}
%
%\cvitem{Software}{\textsc{MySQL}, \textsc{SQLite}, \textsc{phpMyAdmin}, \textsc{Apache}, \textsc{Squid}, \textsc{Origin}, MATLAB}
%\cvitem{System}{\textsc{Windows}, \textsc{Linux} (both \textsc{Debian} and \textsc{Red Hat} based)}

\section{Selected Publications}
\cvitem{2016}{(Daya Bay Collaboration), ``Measurement of the Reactor Antineutrino Flux and Spectrum at Daya Bay", \textit{Phys. Rev. Lett.} 116, 061801 (2016)}

\cvitem{2015}{(Daya Bay Collaboration), ``New Measurement of Antineutrino Oscillation with the Full Detector Configuration at Daya Bay", \textit{Phys. Rev. Lett.} 115, 111802 (2015)}

\cvitem{2013}{Z. Ning, Q.M. Zhang, J.L. Xu, L. Lebanowski, J.W. Zhang, C.G. Yang, M. He, J. Zhao, J.H. Zou, V. P{\v e}{\v c}, \underline{\textbf{\emph{Sh.-K. Lin}}}, M.Y. Guan, H.F. Hao, L. Zheng, X.L. Ji, F. Li, K. Lau and V. Vorobel, ``Calibration algorithms of RPC detectors at Daya Bay Neutrino Experiment", \textit{JINST} 8 (2013) T03007}

@@

%\cvitem{2011}{Liehua Ma, Logan Lebanowski, Jin Chen, Mengyun Guan, Robert Hackenburg, Kwong
%Lau, \underline{\textbf{\emph{Shih-Kai Lin}}}, Changguo Lu, Kirk McDonald, Cullen Newsom, Zhe Ning, Viktor Pec,
%Sen Qian, Vit Vorobel, Yifang Wang, Jilei Xu, Changgen Yang, Jiawen Zhang, Qingmin
%Zhang, “The mass production and quality control of RPCs for the Daya Bay experiment”,
%\textit{Nuclear Instruments and Methods in Physics Research A} 659 (2011) 154–160}
%
%\cvitem{2010}{M. Deniz, S.T. Lin, V. Singh, J. Li, H.T. Wong, S. Bilmis, C.Y. Chang, H.M. Chang, W.C. Chang, C.P. Chen, M.H. Chou, K.J. Dong, J.M. Fang, C.H. Hu, G.C. Jon, W.S. Kuo, W.P. Lai, F.S. Lee, S.C. Lee, H.B. Li, H.Y. Liao, C.W. Lin, F.K. Lin, \underline{\textbf{\emph{S.K. Lin}}}, Y. Liu, J.F. Qiu, M. Serin, H.Y. Sheng, L. Singh, R.F. Su, W.S. Tong, J.J. Wang, P.L. Wang, S.C. Wu, S.W. Yang, C.X. Yu, Q. Yue, M. Zeyrek, D.X. Zhao, Z.Y. Zhou, Y.F. Zhu, and B.A. Zhuang, ``Measurement of $\bar{\nu}_e$-elelctron cross section with a CsI(Tl) scintillating crystal array at the Kuo-Sheng nuclear power reactor", \textit{Phys. Rev. D} 81, 072001 (2010)}
%
%\cvitem{2009}{S.T. Lin, H.B. Li, X. Li, \underline{\textbf{\emph{S.K. Lin}}}, H.T. Wong, M. Deniz, B.B. Fang, D. He, J. Li, C.W. Lin, F.K.
%Lin, V. Singh, X.C. Ruan, J.J. Wang, Y.R. Wang, S.C. Wu, Q. Yue, and Z.Y. Zhou, “New limits
%on spin-independent and spin-dependent couplings of low-mass WIMP dark matter with
%a germanium detector at a threshold of 220 eV”, \textit{Phys. Rev. D} 79:061101, 2009}
%
%\cvitem{2008}{H Y Liao, H M Chang, M H Chou, M Deniz, H X Huang, F S Lee, H B Li, J Li, C W Lin, F K Lin, \underline{\textbf{\emph{S K Lin}}}, S T Lin, V Singh, H T Wong and S C Wu, ``Production and decay of the $^{73}$Ge*(1/2$^-$) metastable state in a low-background germanium detector", \textit{J. Phys. G: Nucl. Part. Phys.} 35 (2008) 077001}
%
%\cvitem{2007}{H. T. Wong, H. B. Li, S. T. Lin, F. S. Lee, V. Singh, S. C. Wu, C.Y. Chang, H. M. Chang, C. P.
%Chen, M. H. Chou, M. Deniz, J. M. Fang, C. H. Hu, H. X. Huang, G. C. Jon, W. S. Kuo, W. P.
%Lai, S. C. Lee, J. Li, H.Y. Liao, F. K. Lin, \underline{\textbf{\emph{S. K. Lin}}}, J. Q. Lu, H.Y. Sheng, R. F. Su, W. S. Tong, B.
%Xin, T. R. Yeh, Q. Yue, Z.Y. Zhou, and B. A. Zhuang, “Search of Neutrino Magnetic
%Moments with a High-Purity Germanium Detector at the Kuo-Sheng Nuclear Power
%Station”, \textit{Phys. Rev. D} 75:012001, 2007}
%\cvitem{2005}{\underline{\textbf{\emph{Shih-Kai Lin}}}, Kun-Ta Wu, Chao-Ping Huang, C.-T. Liang, Y. H. Chang, Y. F. Chen, P. H.
%Chang, N.C. Chen, H. C. Peng, C. F. Shih, K. S. Liu and T. Y. Lin, ``Electron Transport in In-rich In$_x$Ga$_{1-x}$N films", \textit{Journal of Applied Physics} 97, 046101 (2005)}
